%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage[scaled]{helvet}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeExperienceSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \emph{\small#2} & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \multicolumn{2}{l}{\footnotesize#3} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aaryen DSouza} \\ \vspace{1pt}
    \small 437-966-6119 $|$ \href{mailto:dsouza96@uwindsor.ca}{\underline{\phantom{/}dsouza96@uwindsor.ca\phantom{/}}} $|$ 
    \href{https://www.linkedin.com/in/aaryendsouza}{\underline{\phantom{/}linkedin.com/in/aaryendsouza\phantom{/}}} $|$
    \href{https://github.com/aaryen-dsouza}{\underline{\phantom{/}github.com/aaryen-dsouza\phantom{/}}} $|$ 
    \href{https://www.aaryen.vercel.app}{\underline{\phantom{/}Portfolio\phantom{/}}}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, TypeScript, Python, C, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Express, WordPress, Material-UI, Bootstrap, Tailwind CSS} \\
     \textbf{Databases}{:Oracle SQL, PostgreSQL, MySQL, MongoDB} \\
     \textbf{Developer Tools}{: Git, GitHub, Docker, VS Code, IntelliJ, Postman, Microsoft Office, Firebase, Figma, Canva} \\
     \textbf{Other Skills}{: Windows, Linux/Unix (Ubuntu, CentOS), Shell Scripting}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExperienceSubheading
      {Software Engineer}{$|$ Oracle SQL, MS Excel, Bash/Shell Scripting, Java, JavaScript}{July 2022 -- Mar 2024}
      {Vermont Information Processing (Acquired Vistaar US in July 2023)}{Mumbai, India}
      
      \resumeItemListStart
        \resumeItem{Ensured data integrity by conducting data cleaning, preprocessing and validations through Oracle SQL and MS Excel, resolving 95\% of data quality issues within 24 hours, and provided detailed analysis reports to stakeholders.}
        \resumeItem{Reduced issue resolution time by 40\% for 100+ customer reported issues by performing in-depth root cause analysis (RCA) on legacy app server and Oracle database, leading to faster issue identification and customer satisfaction.}
        \resumeItem{Automated ETL workflows by implementing Bash/Shell scripts, optimizing data workflows, and reducing manual interventions by 20\%, which led to improved data onboarding efficiency.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Chat App} $|$ \emph{React, Typescript, Firebase, Zustand, Tailwind CSS, Git}}{Sep 2024}
          {\href{https://github.com/aaryen-dsouza/chat-app}{\underline{GitHub}}}
          \resumeItemListStart
            \resumeItem{Built a real-time chat application using React, TypeScript, and Firebase, enhancing user interaction with an intuitive and responsive UI.}
            \resumeItem{Implemented real-time data synchronization and user activity status tracking (Online, Away, Offline), leading to improved usability and engagement.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Movie App} $|$ \emph{React, ViteJS, Tailwind, Git, TMDb API}}{Apr 2023}
          {\href{https://github.com/aaryen-dsouza/Movie-App}{\underline{GitHub}}}
          \resumeItemListStart
            \resumeItem{Built a React-based movie application using ViteJS and TMDb API, enabling seamless access to comprehensive movie information.}
            \resumeItem{Designed and implemented a responsive UI with Tailwind CSS, improving usability across devices and enhancing the user experience.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Bus Pass Scanner} $|$ \emph{React, NodeJs, Express, MongoDB, Material UI, Git}}{Mar 2022}
          {\href{https://github.com/aaryen-dsouza/BusPass_Scanner}{\underline{GitHub}}}
          \resumeItemListStart
            \resumeItem{Designed and developed a cross-platform bus pass authentication application as part of a 3-member team, enhancing security and efficiency in college transportation.}
            \resumeItem{mplemented a dynamic, responsive UI using React and Material UI, improving accessibility and user experience across devices.}
            \resumeItem{Integrated JWT-based authentication, reducing unauthorized access attempts and strengthening the overall security of the system.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Expenses Manager} $|$ \emph{React, JavaScript, CSS, Git}}{Dec 2021}
          {\href{https://github.com/aaryen-dsouza/Expenses-Manager}{\underline{GitHub}}}
          \resumeItemListStart
            \resumeItem{Developed an expense management web app using React, implementing state management for dynamic list rendering and enhanced user interaction.}
            \resumeItem{Designed and integrated bar chart visualizations to improve financial analysis, helping users gain better insights into their spending patterns.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Windsor}{Windsor, ON}
      {Master of Applied Computing}{May 2024 -- Present}
    \resumeSubheading
      {University of Muumbai}{Mumbai, India}
      {Bachelor of Engineering - Computer Engineering}{Aug 2018 -- May 2022}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
